### 2016-11-15 dissertation/unsat.tex
dissertation version 2_part prelim update 3

\begin{algorithm}[hbt]
\SetAlgoNoLine
	\KwIn{$M$ is the original machine, $p$ is the property to check, $k$ is the number of steps in $k$-BMC}
  $k = $ InitValue\;
  \eIf{$k$-BMC$(M,p,k)$ is \textbf{SAT}}
  {
	\Return{``Found error trace"}
  }
  {
	Extract UNSAT proof $\mathcal P$ of $k$-BMC\;
	$M' = $ \textit{ABSTRACT}$(M,\mathcal P)$\;
  }
  \eIf{MODEL-CHECK$(M',p)$ returns \textbf{PASS}}
  {
	\Return{``Passing property"}
  }
  {
	Increase bound $k$\;
	goto Line 2\;
  }
\caption {Abstraction refinement using $k$-BMC}\label{alg:absrefine}
\end{algorithm}
\begin{figure}[hbt]
\centering{
\includegraphics[width=5.5in]{newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
Assume that we are given a sequential circuit with $n$ latches as shown in Fig.\ref{fig:refine}(a). 
This circuit can be modeled as a Mealy machine $M$ and the states $s$ can be explicitly encoded by bit-level latch variables 
$l_1,\dots,l_n$. Algorithm \ref{alg:absrefine} describes an approach to check if machine $M$ violates property $p$.
This algorithm relies on $k$-BMC technique, which works on the basis of CNF-SAT solving.
The $k$-BMC represents the initial states $I$, the transition relation $T$ and property $p$ as CNF formulas.

>>>>

\IncMargin{1em}
\begin{algorithm}[H]
\SetAlgoNoLine
\LinesNumbered
	\KwIn{$M$ -- original machine, $p$ -- property to check, $k$ -- \# of steps in $k$-BMC}
	\KwOut{If $p$ is violated, return error trace; otherwise $p$ is valid on $M$}
  $k = $ InitValue\;

  \eIf{$k$-BMC$(M,p,k)$ is \textbf{SAT}}
  {
	\Return{``Found error trace"}
  }
  {
	Extract UNSAT proof $\mathcal P$ of $k$-BMC\;
	$M' = $ \textit{ABSTRACT}$(M,\mathcal P)$\;
  }
  \eIf{MODEL-CHECK$(M',p)$ returns \textbf{PASS}}
  {
	\Return{``Passing property"}
  }
  {
	Increase bound $k$\;
	goto Line 2\;
  }
\caption {Abstraction refinement using $k$-BMC}\label{alg:absrefine}
\end{algorithm}
\DecMargin{1em}

\begin{figure}[hbt]
\centering{
\includegraphics[width=5.5in]{newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
Assume that we are given a sequential circuit with $n$ latches as shown in Fig.\ref{fig:refine}(a). 
This circuit can be modeled as a Mealy machine $M$ and the states $s$ can be explicitly encoded by bit-level latch variables 
$l_1,\dots,l_n$. Algorithm \ref{alg:absrefine} describes an approach to check if machine $M$ violates property $p$.
This algorithm relies on $k$-BMC technique, which works on the basis of CNF-SAT solving.
The $k$-BMC represents the initial states $I$, the transition relation $T$ and property $p$ as CNF formulas.
